Subgroup cost analysis

### 2020-08-23 src/subgroup_analysis.Rmd
Add files via upload

---
title: "Subgroup cost analysis"
output: html_notebook
---

```{r setup, echo = FALSE}
setwd("~/interval-sims/src")
library(knitr)
library(dplyr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
source("pffunctions.R")
source("helper_functions.R")
```

>>>>

---
title: "Subgroup cost analysis"
output:
  html_document:
    df_print: paged
---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
setwd("~/interval-sims/src")
library(knitr)
library(dplyr)
library(plyr)
library(lubridate)
library(numbers)
library(data.table)
library(R.utils)
source("pffunctions.R")
source("helper_functions.R")
```
